---
title: "KPIs Marketing"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    navbar:
     - { title: "Portfolio", icon: "fas fa-briefcase", href: "https://roldanramon.github.io/"}
     - { title: "Linkedin", icon: "fab fa-linkedin", href: "https://www.linkedin.com/in/ramon-roldan-de-lara"}
     - { title: "GitHub", icon: "fab fa-github-alt", href: "https://github.com/RoldanRamon"}
     - { title: "WhatsApp", icon: "fab fa-whatsapp", href: "https://api.whatsapp.com/send?1=pt_BR&phone=5541984588355"}
---


```{r setup, include=FALSE, warning=FALSE, message=FALSE}
rm(list = ls())
library(tidyverse)
library(janitor)
library(flexdashboard)
library(DataExplorer)
library(plotly)
library(lubridate)
library(DT)

df_churn <- read_csv('assets/datasets/WA_Fn-UseC_-Telco-Customer-Churn.csv') %>% janitor::clean_names()

```

# About Data

**Telcom Customer Churn - Context:**
"Predict behavior to retain customers. You can analyze all relevant customer data and develop focused customer retention programs." [IBM Sample Data Sets]

**Content:**
The raw data contains 7043 rows (customers) and 21 columns (features).

```{r}
glimpse(df_churn)
```


# BI Analysis

## Linha 1 {data-height=100}

### Total Churn

```{r }
total_churn <- df_churn %>% 
  filter(churn == "Yes") %>% 
  summarise(n()) %>% pull()

valueBox(value = total_churn)
```

### Total Customers

```{r }
total_customers <- df_churn %>% 
  nrow()

valueBox(value = total_customers)
```

### % Churn Rate

```{r }
churn_rate <- round((total_churn / total_customers)*100,digits = 2)

valueBox(value = churn_rate)
```

## linha dois {data-height=300}

### Monthly % Churn Rate

```{r }
p1 <- df_churn %>% 
  group_by(year_month = floor_date(as.Date("2023-02-24"), unit = "month") - months(1) * (tenure - 1)) %>% 
  summarise(churn_rate = round((sum(churn == "Yes") / n())*100,digits = 0)) %>% 
  ungroup() %>% 
  mutate(year = lubridate::year(year_month),
         year_month = forcats::fct_inorder(format(year_month, "%b/%Y"))
          )

plotly::ggplotly(
  ggplot(p1,aes(x = year_month,y = churn_rate, fill = as.factor(year))) +
    geom_col() +
    theme(axis.text.x = element_text(angle = 45)) +
    scale_fill_brewer(palette = "Set1")+
    guides(fill = FALSE)+
    labs(x="",y="")+
    scale_y_continuous(n.breaks = 10)+
    geom_text(aes(label=churn_rate),angle=90)
)
```

## linha tres

```{r }
DT::datatable(df_churn)
```

# Exploratory Analysis (EDA)

## Linha 1

### Plot Vars Types

```{r}
DataExplorer::plot_intro(df_churn)
```


### Plot Missing Values

```{r}
DataExplorer::plot_missing(df_churn)
```


# Statistical Analysis

## Linha 1

### Plot Density

```{r}
DataExplorer::plot_density(df_churn)
```


### Plot Histogram

```{r}
DataExplorer::plot_histogram(df_churn)
```


# Machine Learning

### Classifying Personas through clusters

```{r}
DataExplorer::plot_prcomp(df_churn %>% na.omit())
```

